### 2017-04-16 Paper01_EnthalpyAndCrystallization.tex
Results - added the bulk relaxation images

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{Bulk_Fitted_mValue.png}
	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
	\label{fig:Bulk_Fitted_mValue}
\end{figure}

>>>>

%code to put 2 images side by side in a figure
\begin{figure}[b]
	\centering
	%Image 1
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{Bulk_Relaxed_Full.png}
		\caption{}
		\label{fig:Bulk_Relaxed}
	\end{subfigure}
	%Image 2
	\begin{subfigure}[htbp]{0.495\textwidth}
		\includegraphics[width=\textwidth]{Bulk_Onset_Peaks_Relaxed_120C.png}
		\caption{}
		\label{fig:Bulk_Onsets}
	\end{subfigure}
	\caption{(a) Bulk \MgZnCa~ relaxed at 120 \degree C for 10 minutes and heated at various heating rates. The insert stacks the \gls{dsc} curves and labels the \Tg~ and \Tx es of the $100 K/min$ sample. (b) The \Tg s and \Tx es of the bulk \MgZnCa~ at all heating rates. }%global caption
	\label{fig:DSC_Bulk}
\end{figure}

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{Bulk_Fitted_mValue_Tg.png}
	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
	\label{fig:Bulk_Fitted_mValue}
\end{figure}
